

\documentclass{cv}

\geometry{left=6.1cm,top=1.8cm,right=1.5cm,bottom=0.7cm,nohead,nofoot}


\def\firstname{Benjamin}
\def\familyname{Vial}
\def\FileSubject{curriculum vitae}
\def\FileAuthor{\firstname~\familyname}
\def\FileTitle{\firstname~\familyname's~\FileSubject}
\def\FileKeyWords{\firstname~\familyname, \FileSubject}


\RequirePackage[unicode]{hyperref}% unicode is required for unicode pdf metadata
\hypersetup{
	breaklinks,
	baseurl       = http://,
	pdfborder     = 0 0 0,
	pdfpagemode   = UseNone,% do not show thumbnails or bookmarks on opening
	pdfstartpage  = 1,
	bookmarksopen = true,
	bookmarksdepth= 2,% to show sections and subsections
	pdfauthor   = {\FileAuthor},%
	pdftitle    = {\FileTitle},%
	pdfsubject  = {\FileSubject},%
	pdfkeywords = {\FileKeyWords},%
	pdfcreator  = {\LaTeX},
}



\addbibresource{better.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Benjamin}{~Vial}{Posdoctoral Research Asssistant | Microwave Engineering and Photonics}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
	\section{Contact}
	\faHome~~146 Glyn road
	London E5 0JE, UK
	\faPhone~~+44~7840~029~744
	\faEnvelope~~\href{mailto:b.vial@qmul.ac.uk}{b.vial@qmul.ac.uk}
	\faUser~~\href{http://bvial.info/}{bvial.info}
	\section{Information}
	date of birth 09/11/1984
	French citizenship
	\section{Languages}
	French mother tongue
	English fluent
	Spanish basic
	\section{Programming}
	\textbf{operating systems}
	Linux, Windows
	\textbf{languages and scripts}
	Python, Matlab, Mathematica, \LaTeX, C, C++, Q\#, HTML, CSS
	\textbf{applications}
	git, Comsol Multiphysics, Fenics, Gmsh, GetDP, Gimp, LibreOffice, Labview
	\section{Interests}
	\textbf{professional}
	microwave engineering
	Photonics
	THz physics
	quantum computing
	Transformation Optics
	invisibility cloaking
	light-matter interraction
	computational EM
	numerical modelling
	optimization techniques
	inverse design
	machine learning
	finite element method
	Fourier modal method
	FDTD
	modal analysis
	wave physics
	fabrication
	characterization
	open source science
	\textbf{personal}
	playing the guitar
	listening to music
	football, snowboard, hiking
	traveling, cooking
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
	%------------------------------------------------
	\entry
	{Apr. 2013}
	{PhD {\normalfont in Physics}}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}, CNRS, Centrale Marseille, Aix Marseille Universit\'e, Marseille, France}
	{Optics, Photonics and image processing}
	%------------------------------------------------
	\entry
	{Oct. 2009}
	{Master's degree {\normalfont in Physics}}
	{\href{http://www.centrale-marseille.fr/}{~~Centrale Marseille}~/~
		\href{http://www.lma.cnrs-mrs.fr/}{Laboratoire de Mécanique et d'Acoustique}, CNRS, Marseille, France}
	{Mechanics, Physics and Engineering, specialization in Acoustics}

	\entry
	{Oct. 2009}
	{Master's degree {\normalfont in Engineering}}
	{\href{http://www.centrale-marseille.fr/}{Centrale Marseille}, Marseille, France}
	{High level scientific and technical training}
	%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace*{-0.2cm}
\section{Research activities}

\begin{entrylist}
	%------------------------------------------------



	\entry
	{Jan. 2019 \\Now}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{\href{https://animate-research.com/}{ANIMATE project}: nonlinear coupling model and homogenization of ferroelectric
		metamaterials, inverse design for tunability enhancement, microwave and THz material characterization.
	}


	\entry
	{Jan. 2017 \\Dec. 2018}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{AOTOMAT project : Optimization tools and machine learning for the design of electromagnetic
		devices and materials.
	}

	\entry
	{Jul. 2014 \\Dec. 2016}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{\href{http://www.quest-spatial-transformation.org/}{QUEST project: Quest for Ultimate Electromagnetics Using Spatial Transformations.}
		Transformation Optics applied to the design, fabrication and characterization of novel electromagnetic devices using metamaterials.
		Development of simulation tools and optimization techniques.
	}


	\entry
	{Nov. 2013\\ Jan. 2014}
	{Postdoctoral Research Assistant}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}, Marseille, France}
	{
		Numerical study of the coupling of light
		to subwavelength resonant optical antennas and control of the local density of states.
	}
	%------------------------------------------------
	\entry
	{May 2013 \\Oct. 2013}
	{Postdoctoral Research Assistant}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}, Marseille, France}
	{
		Development of simulation tools for ray tracing in complex media, inverse problem of
		finding index distribution to make light follow a prescribed path, deshomogenization
		technique with graded index photonic crystals.
	}

	%------------------------------------------------
	\entry
	{Oct. 2009\\Apr. 2013}
	{PhD in Physics}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}~--~\href{http://www.silios.com/}{Silios Technologies}, Marseille, France}
	{\emph{\href{http://tel.archives-ouvertes.fr/index.php?halsid=slas337fv1oqlj1okgkq7q42i5&view_this_doc=tel-00918651&version=1}
			{Study of open electromagnetic resonators by modal approach.
				Application to infrared multispectral filtering.}} (\emph{joint academia/industry funding})\\
		FEM modelling of metamaterials, spectral analysis quasi-normal mode expansion.
		Application to the design of infrared filters for multispectral imaging devices.
		Fabrication and characterization of reflexion bandcut and transmission bandpass filters.
	}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	Teaching/supervising experience SECTION
%----------------------------------------------------------------------------------------

\vspace*{-0.2cm}
\section{Teaching/supervising experience}

\begin{entrylist}
	%------------------------------------------------
	\entry
	{2011-2012}
	{Internship supervisor}
	{{Institut Fresnel}, CNRS, Centrale Marseille, Marseille, France}
	{Optimization of diffractive spectral infrared filters (1 engineer student, 6 months).\\
		Optimization of absorption in solar cells (4 engineer students, 3 months).
	}

	%------------------------------------------------
	\entry
	{2019}
	{Teaching Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{Quantum Programming. Lectures and tutorials on quantum gates and circuits.
		Coding laboratory and projects in Q\# an Python (10 Master students, 6 months).}

	%------------------------------------------------

\end{entrylist}

\vspace*{-0.2cm}
\section{Awards and honours}

  {Best PhD thesis 2014 award} from the {\href{https://ecole-doctorale-352.univ-amu.fr/en}{Doctoral School 352, Physics and Condensed Matter Science}}

  {Best PhD thesis 2014 award from {\href{https://www.cnano-paca.fr/index.php?option=com_content&view=article&id=80}{CNano PACA}}, finalized research category}



\newgeometry{left=1.5cm,top=1.8cm,right=1.5cm,bottom=0.7cm,nohead,nofoot}



%----------------------------------------------------------------------------------------
%	Referees contact SECTION
%----------------------------------------------------------------------------------------


\section{Referees contact}

\begin{minipage}{.6\textwidth}
	\textbf{Prof Yang Hao}\\
	\faHome~~School of Electronic Engineering and Computer Science\\
	Queen Mary University of London\\
	Peter Landin Building, 10 Godward Square, Mile End Road\\
	London E1 4FZ, United Kingdom\\
	\faEnvelope~~\href{mailto:y.hao@qmul.ac.uk}{y.hao@qmul.ac.uk}\\
	\faPhone~~+44 20 7882 5341\\
	\faUser~~\href{http://www.eecs.qmul.ac.uk/~yang/}{www.eecs.qmul.ac.uk/~yang/}
\end{minipage}%
\begin{minipage}{0.4\textwidth}
	\textbf{Prof Andr\'e Nicolet}\\
	\faHome~~Aix-Marseille Université\\
	Institut Fresnel (UMR CNRS 6133)\\
	Domaine Universitaire de Saint-Jérôme\\
	F13397 Marseille cedex 20, France\\
	\faEnvelope~~\href{mailto:andre.nicolet@fresnel.fr}{andre.nicolet@fresnel.fr}\\
	\faPhone~~+33 4 91 28 87 73\\
	\faUser~~\href{https://www.fresnel.fr/perso/nicolet/}{www.fresnel.fr/perso/nicolet/}
\end{minipage}


\vspace*{0.5cm}

%----------------------------------------------------------------------------------------
%	Publications SECTION
%----------------------------------------------------------------------------------------


\section{Publications}

\printbibsection{article}{Articles in peer-reviewed journals}

\printbibsection{book}{Contribution to book chapter}

\printbibsectionkey{inproceedings}{Proceedings of international peer-reviewed conferences}{lecture comittee}

\printbibsectionkey{inproceedings}{International peer-reviewed conferences}{conference}

\printbibsectionkey{misc}{PhD thesis}{phdthesis}

\printbibsectionkey{misc}{Open source software and code}{code}

\printbibsectionkey{misc}{In preparation}{prep}


\end{document}
