

\documentclass{cv}

\geometry{left=6.0cm,top=1.8cm,right=1.5cm,bottom=0.7cm,nohead,nofoot}

\addbibresource{better.bib} % Specify the bibliography file to include publications


\def\firstname{Benjamin}
\def\familyname{Vial}
\def\FileSubject{cover letter}
\def\FileAuthor{\firstname~\familyname}
\def\FileTitle{\firstname~\familyname's~\FileSubject}
\def\FileKeyWords{\firstname~\familyname, \FileSubject}

  \RequirePackage[unicode]{hyperref}% unicode is required for unicode pdf metadata
  \hypersetup{
    breaklinks,
    baseurl       = http://,
    pdfborder     = 0 0 0,
    pdfpagemode   = UseNone,% do not show thumbnails or bookmarks on opening
    pdfstartpage  = 1,
%    pdfproducer   = {\LaTeX{}},% will/should be set automatically to the correct TeX engine used
    bookmarksopen = true,
    bookmarksdepth= 2,% to show sections and subsections
    pdfauthor   = {\FileAuthor},%
    pdftitle    = {\FileTitle},%
    pdfsubject  = {\FileSubject},%
    pdfkeywords = {\FileKeyWords},%
    pdfcreator  = {\LaTeX},%
    pdfproducer = {\LaTeX}
    }


\begin{document}


\header{Benjamin}{~Vial}{Posdoctoral Research Asssistant | Mathematical Modelling and Wave Physics}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------


\begin{aside} % In the aside, each new line forces a line break
	\section{Contact}
	\faHome~~146 Glyn road
	London E5 0JE, UK
	\faPhone~~+44~7840~029~744
	\faEnvelope~~\href{mailto:b.vial@imperial.ac.uk}{b.vial@imperial.ac.uk}
	\faUser~~\href{http://bvial.info/}{bvial.info}
	\section{Information}
	date of birth 09/11/1984
	French citizenship
	\section{Languages}
	French mother tongue
	English fluent
	Spanish basic
	\section{Programming}
	\textbf{operating systems}
	Linux, Windows
	\textbf{languages and scripts}
	Python, Matlab, Mathematica, \LaTeX, C, C++, Q\#, HTML, CSS
	\textbf{applications}
	git, Comsol Multiphysics, Fenics, Gmsh, GetDP, Gimp, LibreOffice, Labview
	\section{Interests}
	\textbf{professional}
	Optics
	Photonics
	Metamaterials
	wave physics
	light-matter interraction
	homogenization methods
	computational EM
	numerical modelling
	optimization techniques
	inverse design
	finite element method
	Fourier modal method
	modal analysis
	machine learning
	Transformation Optics
	invisibility cloaking
	fabrication
	characterization
	open source science
	\textbf{personal}
	playing the guitar
	listening to music
	football, snowboard, hiking
	traveling, cooking
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
	%------------------------------------------------
	\entry
	{Apr. 2013}
	{PhD {\normalfont in Physics}}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}, CNRS, Centrale Marseille, Aix Marseille Universit\'e, Marseille, France}
	{Optics, Photonics and image processing}
	%------------------------------------------------
	\entry
	{Oct. 2009}
	{Master's degree {\normalfont in Physics}}
	{\href{http://www.centrale-marseille.fr/}{~~Centrale Marseille}~/~
		\href{http://www.lma.cnrs-mrs.fr/}{Laboratoire de Mécanique et d'Acoustique}, CNRS, Marseille, France}
	{Mechanics, Physics and Engineering, specialization in Acoustics}

	\entry
	{Oct. 2009}
	{Master's degree {\normalfont in Engineering}}
	{\href{http://www.centrale-marseille.fr/}{Centrale Marseille}, Marseille, France}
	{High level scientific and technical training}
	%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace*{-0.2cm}
\section{Research activities}

\begin{entrylist}
	%------------------------------------------------

	\entry
	{Aug. 2022 \\Now}
	{Postdoctoral Research Assistant}
	{\href{http://imperial.ac.uk/}{Imperial College London}, London, UK}
	{\href{https://www.metaveh.com/}{METAVEH project}: Mathematical modelling of mechanical waves for energy harvesting using metamaterials. High frequency homogenization in dispersive media.
	}


	\entry
	{Jan. 2019 \\Aug. 2022}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{\href{https://animate-research.com/}{ANIMATE project}: nonlinear coupling model and homogenization of ferroelectric
		metamaterials, inverse design for tunability enhancement, microwave and THz material characterization.
	}


	\entry
	{Jan. 2017 \\Dec. 2018}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{AOTOMAT project : Optimization tools and machine learning for the design of electromagnetic
		devices and materials.
	}

	\entry
	{Jul. 2014 \\Dec. 2016}
	{Postdoctoral Research Assistant}
	{\href{http://antennas.eecs.qmul.ac.uk/}{Queen Mary, University of London}, London, UK}
	{\href{http://www.quest-spatial-transformation.org/}{QUEST project: Quest for Ultimate Electromagnetics Using Spatial Transformations.}
		Transformation Optics applied to the design, fabrication and characterization of novel electromagnetic devices using metamaterials.
		Development of simulation tools and optimization techniques.
	}


	\entry
	{May. 2013\\ Jan. 2014}
	{Postdoctoral Research Assistant}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}, Marseille, France}
	{		Development of simulation tools for ray tracing in complex media, inverse problem of
	finding index distribution to make light follow a prescribed path, deshomogenization
	technique with graded index photonic crystals.
		Numerical study of the coupling of light
		to subwavelength resonant optical antennas and control of the local density of states.
	}

	%------------------------------------------------
	\entry
	{Oct. 2009\\Apr. 2013}
	{PhD in Physics}
	{\href{http://www.fresnel.fr/}{Institut Fresnel}~--~\href{http://www.silios.com/}{Silios Technologies}, Marseille, France}
	{\emph{\href{http://tel.archives-ouvertes.fr/index.php?halsid=slas337fv1oqlj1okgkq7q42i5&view_this_doc=tel-00918651&version=1}
			{Study of open electromagnetic resonators by modal approach.
				Application to infrared multispectral filtering.}} (\emph{joint academia/industry funding})\\
		FEM modelling of metamaterials, spectral analysis quasi-normal mode expansion.
		Application to the design of infrared filters for multispectral imaging devices.
		Fabrication and characterization of reflexion bandcut and transmission bandpass filters.
	}

\end{entrylist}

\vspace*{-0.3cm}
\section{Awards and honours}

  {Best PhD thesis 2014 award} from the {\href{https://ecole-doctorale-352.univ-amu.fr/en}{Doctoral School 352, Physics and Condensed Matter Science}}

  {Best PhD thesis 2014 award from {\href{https://www.cnano-paca.fr/index.php?option=com_content&view=article&id=80}{CNano PACA}}, finalized research category}


  \nocite{vial2022open,vial2016class,VialQMEM}
  
\printbibliography[title=Selected publications]

\end{document}
